### 2008-03-21 trunk/Papers/dl-gre-08/gre.tex
small stuff

The pseudocode for our \alc\ algorithm is shown as
Algorithm~\ref{algo:bisim-l} and Algorithm~\ref{algo:bisim-add-alc}.
Given a model $\gM=(\Delta, \interp{\cdot})$, the algorithm computes a
set $\RE$ of $\alc$ formulas such that the set $\{\interp{\varphi}
\mid \varphi \in \RE\}$ is the set of \alc-similarity sets of $\gM$.
The algorithm starts with $\RE = \{\top\}$ (where $\interp{\top} =
\Delta$), and successively refines $\RE$ by making its elements denote
smaller and smaller sets.  It maintains the invariant that at the
start and end of every iteration, $\{\interp{\varphi} \mid \varphi \in
\RE\}$ is always a partition of $\Delta$.  The algorithm iterates over
all propositional and relational symbols of the signature to construct
new formulas until either all formulas in $\RE$ denote singletons
(i.e., there is only one individual that satisfies them), or no
progress has been made in the previous iteration.  In each iteration,
it calls the procedure add$_\alc$($\varphi$, $\RE$), which intersects
$\varphi$ with any formula $\psi \in \RE$ which does not denote a
singleton and which is not equivalent to $\varphi$ and to $\neg
\varphi$. In this case, it replaces $\psi$ in $\RE$ by $\psi \sqcap
\varphi$ and $\psi \sqcap \neg \varphi$.

The \alc\ algorithm is capable of computing the \alc-similarity sets
of the model very efficiently, in time $O(nm)$ where $n$ is the number
of individuals in the domain, and $m$ is the number of pairs of
individuals that are related by some relation.  However, it will
freely introduce negations in the case distinctions, which can make
the resulting formula hard to realize (see also
Section~\ref{sec:discussion-realization}).  This is why we also
present an algorithm for the \el-similarity sets; \el\ corresponds to
positive relational REs, which are generally much easier to realize.

>>>>

The pseudocode for our \alc\ algorithm is shown as
Algorithm~\ref{algo:bisim-l} and Algorithm~\ref{algo:bisim-add-alc}.
Given a model $\gM=(\Delta, \interp{\cdot})$, the algorithm computes a
set $\RE$ of $\alc$ formulas such that $\{\interp{\varphi} \mid
\varphi \in \RE\}$ is the set of \alc-similarity sets of $\gM$.  The
algorithm starts with $\RE = \{\top\}$ (where $\interp{\top} =
\Delta$), and successively refines $\RE$ by making its elements denote
smaller and smaller sets.  It maintains the invariant that at the
start and end of every iteration, $\{\interp{\varphi} \mid \varphi \in
\RE\}$ is always a partition of $\Delta$.  The algorithm iterates over
all propositional and relational symbols in $\prop$ and $\rel$ to
construct new formulas until either all formulas in $\RE$ denote
singletons (i.e., there is only one individual that satisfies them),
or no progress has been made in the previous iteration.  In each
iteration, it calls the procedure add$_\alc$($\varphi$, $\RE$), which
intersects $\varphi$ with any formula $\psi \in \RE$ which does not
denote a singleton and which is not equivalent to $\varphi$ and to
$\neg \varphi$. In this case, it replaces $\psi$ in $\RE$ by $\psi
\sqcap \varphi$ and $\psi \sqcap \neg \varphi$.

The \alc\ algorithm is capable of computing the \alc-similarity sets
of the model in time $O(nm)$, where $n$ is the number of individuals
in the domain, and $m$ is the number of pairs of individuals that are
related by some relation.  However, it will freely introduce negations
in the case distinctions, which can make the resulting formula hard to
realize (see also Section~\ref{sec:discussion-realization}).  This is
why we also present an algorithm for the \el-similarity sets; \el\
corresponds to positive relational REs, which are generally much
easier to realize.
